artData

### 2018-01-16 docs/articles/dataMaid_artData.Rmd
Added initial prototype for makeCodebook

---
dataMaid: yes
title: artData
subtitle: "Autogenerated data summary from dataMaid"
date: 2017-12-21 01:29:36
output: html_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
```{r visualFunctions, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:

@@

 *  Report creation time: Thu Dec 21 2017 01:29:36

@@

 *  Platform: x86_64-apple-darwin15.6.0 (64-bit)(macOS High Sierra 10.13.1).

>>>>

---
dataMaid: yes
title: artData
subtitle: "Autogenerated data summary from dataMaid"
date: 2018-01-12 19:32:44
output: html_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
```{r visualFunctions, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:

@@

 *  Report creation time: Fri Jan 12 2018 19:32:44

@@

 *  Platform: x86_64-apple-darwin15.6.0 (64-bit)(macOS High Sierra 10.13.2).
